### 2017-02-08 thesis/latex/thesis.tex
Add feature for printing only onebound states, to debug why they're behaving weird.

\section{Chapter: Introduction}
%% Begin with a paper-like introduction which talks about:

@@

\subsubsection{ATP binding / unbinding effects}
\subsubsection{Microtubule un/rebinding}

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
  \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
  \label{dynein-artist-rendition-2}
\end{figure}

@@

\subsubsection{Other theories?}
Imamula model: how it is different from Cianfrocco model, and why we chose the Cianfrocco model.\\
	\subsection{Past Simulations}
		\subsubsection{Sarlah Winch Model}
		\subsubsection{-x Other models}
	\subsection{Brownian motion}
                \subsubsection{Introduction/derivation}
                \subsubsection{Justification}

\subsection{Simulation}
Talk about why simulation is the only way to verify the mechanochemical cycle, since experiments
aren't high resolution enough to make good videos of the walk, and even if they were, in some sense
knowing that dynein behaves identically to a simple mathematical model is more informative than
a video, since there is lots of information in a video and really precise info in a simulation.\\

@@

\subsection{Our model}
Talk about what the important parts of the mechanochemical cycle from the introduction are, and how
we take those and model them.\\
\subsubsection{Rigid point model}
Talk about two things: reducing bulky circular domains to points (is this the same as unified atom
model?) with a certain drag constant based on radius, and acting like the domains are rigid in
distance from each other. Talk about why this is valid (is it? it's an assumption, David may know
more).
\subsubsection{Harmonic energies}
How we're modeling the complicated folding and adjusting of a massive protein as a harmonic
oscillator. Why this is valid. Also other approaches...what else could we have modelled it as?
\subsubsection{Two-state model}
The mechanochemical cycle has eight states. We choose two as representative because \textbf{a.)}
many of the states are identically conformationally or \textbf{b.)} the transitions happen so fast
the intermediate states don't matter. Talk about rate constants here.
\subsubsection{Limitations}
Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information,
other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into
account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be
springy...

Mention the Burgess paper, which says spring constants might change between apo/ADP states.

\paragraph{Gibbs energy of transition}
Do some stuff with Gibb's here? Why our energies are Gibb's and not internal energy?\\

\section{Chapter: Theory}
\subsection{Dynein Models}
In order to simulate a protein's passage through the above mechanochemical cycle, two mathematical models are needed: one for the prestroke, MTBD-detached state, and one for the poststroke, MTBD-bound state. The purpose of each model is to calculate the position and velocity of each domain at an arbitrary time.\\

@@

\subsection{Other ways to represent data?}

\section{Chapter: Discussion}
\subsection{Why our model worked, didn’t work}
Fill this out over winter when you know more.\\
\subsection{Future work on this project}
If setbacks happen, this'll be a big section. Or, further simulations which could be done.

>>>>

\section{Chapter: Introduction}

%% Begin with a paper-like introduction which talks about:

@@

\subsubsection{ATP binding / unbinding effects}
\subsubsection{Microtubule un/rebinding}
Microtubule binding and unbinding play an important role in the dynein mechanochemical cycle. The MTBD/stalk system has two conformational states: a high-MT-affinity state where MT binding occurs at a fast rate, and a low-affinity state with a slower binding rate \. The MTBD/stalk alternates between these two states as the motor progresses through the mechanochemical cycle

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
  \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}. Is this figure actually useful, or would a diagram be better?}
  \label{dynein-artist-rendition-2}
\end{figure}

@@

\subsubsection{Other theories?}
Imamula model: how it is different from Cianfrocco model, and why we chose the Cianfrocco model.\\
	\subsection{Past Simulations}
		\subsubsection{Sarlah Winch Model}
		\subsubsection{Other models}

\subsection{Moving forward}
Talk about why simulation is the only way to verify the mechanochemical cycle, since experiments
aren't high resolution enough to make good videos of the walk, and even if they were, in some sense
knowing that dynein behaves identically to a simple mathematical model is more informative than
a video, since there is lots of information in a video and really precise info in a simulation.\\

@@

\section{Chapter: Theory}
\subsection{Model features}
Talk about what the important parts of the mechanochemical cycle from the introduction are, and how
we take those and model them.\\
\subsubsection{Rigid point model}
Talk about two things: reducing bulky circular domains to points (is this the same as unified atom
model?) with a certain drag constant based on radius, and acting like the domains are rigid in
distance from each other. Talk about why this is valid (is it? it's an assumption, David may know
more).
\subsubsection{Harmonic energies}
How we're modeling the complicated folding and adjusting of a massive protein as a harmonic
oscillator. Why this is valid. Also other approaches...what else could we have modelled it as?
\subsubsection{Two-state model}
The mechanochemical cycle has eight states. We choose two as representative because \textbf{a.)}
many of the states are identically conformationally or \textbf{b.)} the transitions happen so fast
the intermediate states don't matter. Talk about rate constants here.

\subsection{Brownian motion}
\subsubsection{Introduction/derivation}
\subsubsection{Justification}

\subsection{Mathematical models}
In order to simulate a protein's passage through the above mechanochemical cycle, two mathematical models are needed: one for the prestroke, MTBD-detached state, and one for the poststroke, MTBD-bound state. The purpose of each model is to calculate the position and velocity of each domain at an arbitrary time.\\

@@

\section{Chapter: Discussion}
\subsubsection{Limitations}
Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information,
other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into
account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be
springy...

Mention the Burgess paper, which says spring constants might change between apo/ADP states.
\subsection{Future work on this project}
If setbacks happen, this'll be a big section. Or, further simulations which could be done.
